### 2018-07-08 FrascatiPlot/Paper/NucleiB2.tex
major change: adding figure 4 to the paper and restructuring it for emergency to a first publication which will then be followed up by one explicitly for predictions. Like this the formalism can be kept separate from the studies for the yellow report.

 \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}
 - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm

 \subsection{Predictions for A=4}
 - add a plot for A=4

 \subsection{Other exotic QCD objects}
 - add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature. One of them is the X(3872) which might have a wide wave-function as described in http://inspirehep.net/record/861896?ln=de

\section{Projections for the LHC Run 3 and 4}\label{sec:projections}

\section{Summary and conclusions}

@@

>>>>

 \subsection{Thermal and coalescence model for A=2,3 anti- and hyper-nuclei}
 - add a three-panel plot for deuteron, he and hyper-triton with different radii for hyper-triton from 10fm to 3fm and for the excited state of the hyper-triton!!

\begin{figure}[htbp]
	\begin{center}
		\includegraphics[width=\textwidth]{compareThermalAndCoalescence.png}
		\caption{Comparison of the ALICE data from~\cite{ALICE:deuteronppPbPb2015,ALICE:nucleipp2017} with the thermal model expectations and the coalescence prediction which is tuned to \btwo\ values in central Pb-Pb collisions.}
		\label{fig:CompareThermalAndCoalescence}
	\end{center}
\end{figure}
 %\subsection{Predictions for A=4}
 %- add a plot for A=4

 %\subsection{Other exotic QCD objects}
 %- add a plot for the X(3872)???? --> Look at the ExHic and Maiani rebuttal
%We can consider essentially all Objects proposed by the ExHIC collaboration if they are of a composite nature or might be of a composite nature. One of them is the X(3872) which might have a wide wave-function as described in http://inspirehep.net/record/861896?ln=de

%\section{Projections for the LHC Run 3 and 4}\label{sec:projections}

\section{Summary, conclusions, and outlook}

@@

In a follow-up publication, we will extend the study presented here to predictions for the $A$=4 systems introduced in Tab.~\ref{table} and to more exotic QCD objects like the X(3827). These predictions will be of outmost importance for the currently prepared physics case for LHC Run 3 \& 4 and beyond.
